---
title: "Data 607 Character Manipulation and Date Processing"
author: "Wilson Chau"
date: "2022-09-16"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

#1. Using the 173 majors listed in fivethirtyeight.com's College Majors
dataset
[<https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/>],
provide code that identifies the majors that contain either "DATA" or
"STATISTICS" Finding major with the word "Data"

```{r}
library(stringr)
Word_Data_or_Stat <-read.csv("https://raw.githubusercontent.com/Wilchau/Data607assignment3/main/Major%20list.csv%20-%20Sheet1.csv",header = TRUE, sep = ",")
```

```{r}
Words_Data <- str_detect(Word_Data_or_Stat$Major, fixed("DATA"))
Word_Data_or_Stat[Words_Data,]
```

```{r}
Words_STAT <-str_detect(Word_Data_or_Stat$Major, fixed("STATISTICS"))
Word_Data_or_Stat[Words_STAT,]
```

Utilizing str_detect I was able to find a total of 3 majors that can had
Data OR Statistics. #2 Write code that transforms the data below: [1]
"bell pepper" "bilberry" "blackberry" "blood orange" [5] "blueberry"
"cantaloupe" "chili pepper" "cloudberry"\
[9] "elderberry" "lime" "lychee" "mulberry"\
[13] "olive" "salal berry" Into a format like this: c("bell pepper",
"bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe",
"chili pepper", "cloudberry", "elderberry", "lime", "lychee",
"mulberry", "olive", "salal berry")

```{r}
unorganized_fruits <- '“bell pepper” “bilberry” “blackberry” “blood orange”
“blueberry” “cantaloupe” “chili pepper” “cloudberry”
“elderberry” “lime” “lychee” “mulberry”
“olive” “salal berry”'

organized_fruits<- paste('c(', paste('"',unorganized_fruits,'"',sep = "", collapse = ','), sep = "",')')
organized_fruits
```

#3 Describe, in words, what these expressions will match: #This will
match any one character, followed by two repetitions, like "aaa" or
"555". The correct expression would

1)  (.)\\1\\1

    This can be a regular expression is used to match a pattern in a
    string with the same character appearing three times in a row.
    Example: 777,www

2)  "(.)(.)\\2\\1"

    Matches the 2 strings or character group follow by '\\2\\1'.
    Example: ab\\2\\1

3)  (..)\\1

    This can match with any two characters before \\1. Example: aa\\1

4)  "(.).\\1.\\1"

    A character followed by any character, the original character, any
    other character, and the original character again. Example: a\\1b\\1

5)  "(.)(.)(.).\*\\3\\2\\1"

    This can match with 3 characters followed by zero or more characters
    of any kinds followed by the same three characters in reverse.
    Example: abc\\3\\2\\1

#4 1)Construct regular expressions to match words that: 1)Start and end with the same character.
str_match(exercise_four,'^(.).*\\1$')

2)Contain a repeated pair of letters (e.g. "church" contains "ch"
repeated twice.) \`\`\`
str_bring(exercise_four_two, "(..).*\\1")


3)Contain one letter repeated in at least three places (e.g. "eleven"
contains three "e"s.) \`\`\`
str_bring(exercise_four_three, "([a-z]).*\\1.*\\1")